---
title: "Gapminder Analysis"
author: "Data Services @ HSL"
date: "10/14/2019"
output: 
  html_document:
    keep_md: yes
    fig_caption: yes
    toc: yes
---

# Introduction

Here is my first rmd document

# Let's embed some r code

We'll write an R chunk that loads the tidyverse package and then reads in the Gapminder data set from the data subdirectory of the project

CMD + OPT + i
CNTRL + ALT + i to insert new r chunk
```{r, message=FALSE}
library(tidyverse)
gm <- read_csv("Data/gapminder.csv")
```

# Investigate gm data

Let's take a look at the gm

```{r}
head(gm)
```

# Our first plot

Showing gdp per captia on x and life expectancy on y

```{r, fig.cap="Life Expectancy v. GDP"}
ggplot(gm, aes(x = gdpPercap, y = lifeExp)) + geom_point()
```

# A better plot

```{r, fig.cap="Life Expectancy v. GDP with color", fig.width=3}
ggplot(gm, aes(x = gdpPercap, y = lifeExp)) + 
  geom_point(aes(col = continent)) +
  scale_x_log10()
```

# Possible chunk options

Options include:
- echo (TRUE by default) whether to include code in output
- results 
  - hide will hide the results
  - hold will hold results until end of r chunk
- include (TRUE by default) if FALSE then the code will not be run
- fig.width, fig.height set the figure dimensions in the output
- cache (FALSE by default) if TRUE saves result from R chunk

# Table in RMarkdown

See some data using head

```{r}
head(gm)
```

now head function as a nicely formatted table

```{r}
library(knitr)
kable(head(gm))
```

If you like tables, look at **gt** table package
